%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, linkcolor=blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Yuqi Xie} \\ \vspace{1pt}
    1859 Shirley Ln Apt B7, Ann Arbor, MI, 48105 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 734-510-4285 ~ \href{mailto:xieleo@umich.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{xieleo@umich.edu}} ~ 
    %\href{https://linkedin.com/in//}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/username}}  ~
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/xieleo5}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Michigan, Ann Arbor}{Sep. 2021 -- Apr. 2023(Expected)}
      {Bachelor of Computer Science - College of Engineering}{Ann Arbor, Michigan, U.S.}
    \begin{itemize}
      \item \textbf{Admitted Transfer Student of the Dual Degree Program}
      \item \textbf{GPA: }3.96/4.0
    \end{itemize}
    \vspace*{4.0\multicolsep}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {Shanghai Jiaotong University}{Sep. 2019 -- Aug. 2021}
      {Bachelor of Electrical and Computer Engineering - UM-SJTU Joint Institute}{Shanghai, China}
  \resumeSubHeadingListEnd
% %------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     %\resumeSubHeadingListStart
%     \begin{itemize}[itemsep=-3pt, parsep=3pt]
%         \item Programming: EECS 281(A+), EECS 370(A+), EECS 376 (A), EECS 481(A-), EECS 388(A), EECS 482(A), EECS 493(In Progress), EECS 485(In Progress), EECS 498-003(XR, In Progress)
%         \item Machine Learning: EECS 545(A), EECS 498-008(CV, A), CS224n(free lecture online)
%     \end{itemize}
%     %
%     %\resumeSubHeadingListEnd

\section{Interested Area}
%\resumeSubHeadingListStart
\begin{itemize}[itemsep=-3pt, parsep=3pt]
    \item Artificial Intelligence, Reinforcement Learning, Multi-Modal Machine Learning.
    \item Software Engineering.
    \item Extended Reality (VR and AR).
\end{itemize}

% -----------EXPERIENCE-----------
\section{Experience}
 \resumeSubHeadingListStart

   \resumeSubheading
     {MineDojo Team}{April 2022 - Present}
     {Undergraduate Research Assistant}{\href{https://github.com/MineDojo}{Github Website}}
     \resumeItemListStart
       \resumeItem{Developed a \href{https://github.com/openai/gym}{Gym} environment called FabricDojo for Reinforcement Learning agent based on \href{https://fabricmc.net/}{Fabric}. It is similar to Microsoft's \href{https://github.com/minerllabs/minerl}{MineRL}, but change the action space to be only mouse and keyboard.}
       \resumeItem{Developed a web browsing Gym environment based on \href{https://www.selenium.dev/}{Selenium}.}
       \resumeItem{Update MineDojo to MineDojo2 using the new MineRL v1.0 backend, which is based on \href{https://github.com/Hexeption/MCP-Reborn}{MCP-Reborn}}
     \resumeItemListEnd

   \resumeSubheading
   {SOCR MDP Team}{Winter Semester, 2022}
     {Undergraduate Research Assistant}{\href{https://www.socr.umich.edu/}{Official Website}}
     \resumeItemListStart
       \resumeItem{Help to clean up the MIMIC-III dataset. Remove unused columns and punctuations. }
       \resumeItem{Finetune scikit-learn's pre-trained word2vec language model on MIMIC-III dataset.}
       \resumeItem{Use the finetuned model to obfuscate the personal information in hospital's database.}
   \resumeItemListEnd
   
 \resumeSubHeadingListEnd
\vspace{-16pt}
%
%-----------PROJECTS-----------
\section{Previous Works}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{MineDojo2} $|$ \emph{Python, Gym, Java, Gradle, Jinja2 | Research Project}}{On-going project}
        \resumeItemListStart
          \resumeItem{MineDojo2 is based on MineRL's \href{https://github.com/minerllabs/minerl/releases/tag/v1.0}{new v1.0 backend}. It inherited all of the \href{https://docs.minedojo.org/}{MineDojo's api}, and have better support for mouse and keyboard actions.}
          \resumeItem{The game version is updated to v1.16.5, and there are more observation spaces.}
          \resumeItem{Support OpenAI's \href{https://github.com/openai/Video-Pre-Training}{VPT} pre-trainned model, can train new agent based on that easily.}
          % \resumeItem{The action space more focus on low-level input like mouse and keyboard, so that the agent can act more like a human.}
        \resumeItemListEnd
        \vspace{-13pt}
      \resumeProjectHeading
        {\textbf{Contribution to MineRL} $|$ \emph{Python, Java , Gym| Personal Contribution}}{Summer Break, 2022}
        \resumeItemListStart
          \resumeItem{MineRL v1.0 was released in August. It completely reformat its backend so many of its APIs are not working.}
          \resumeItem{Fix the problem that the life status observation always return the default value. \href{https://github.com/minerllabs/minerl/pull/664}{Link to PR}}
          \resumeItem{Implement the equipped item observation on java side, also fix problem of same observation on python side. \href{https://github.com/minerllabs/minerl/pull/665}{Link to PR}}
        \resumeItemListEnd
        \vspace{-13pt}
      \resumeProjectHeading
        {\textbf{FabricDojo} $|$ \emph{Python, Gym, Java, GRPC, Mixin, Gradle | Research Project}}{Summer Break, 2022}
        \resumeItemListStart
          \resumeItem{FabricDojo is a Gym enviroment for Reinforcement Learning agent to play Minecraft. It is based on Fabric, which is a mod maker of Minecraft.}
          \resumeItem{Use GRPC and localhost socket to communicate between Java and python, run 2 times faster than Microsoft MineRL in benchmark.}
          \resumeItem{Unlike Microsoft MineRL only use Minecraft 1.12, it can be used on the latest Minecraft Game and can be updated to new version easily. }
          \resumeItem{The action space more focus on low-level input like mouse and keyboard, so that the agent can act more like a human.}
        \resumeItemListEnd
        \vspace{-13pt}
      \resumeProjectHeading
        {\textbf{SOCR-DataSifter} $|$ \emph{Python | MDP SOCR Project}}{Winter Semester, 2022}
        \resumeItemListStart
          \resumeItem{\href{https://socr.umich.edu/HTML5/DataSifter/}{DataSifter} is a method to share real clinical data containing clearly identifiable personal health information (PHI) without compromising either the value of the data or by introducing a substantial risk for re-identification of individuals.}
          \resumeItem{Use LightGBM to find out keywords that contibute most to the information that need to be obfuscated.}
          \resumeItem{Finetune language model on MIMIC-III dataset. Obfuscate the data using the language model by finding synonymous substitution.}
          \resumeItem{Use SDV Privacy-Utility metrics to evaluate the effect of the whole model.}
        \resumeItemListEnd
        \vspace{-13pt}
      \resumeProjectHeading
        {\textbf{Arceus} $|$ \emph{Python, Gym | Personal Project}}{Winter Semester, 2022}
        \resumeItemListStart
          \resumeItem{A Gym environment for agent to play with Pokemon Gold. The simulator is based on \href{https://openai.com/blog/gym-retro/}{Gym Retro}.}
          \resumeItem{The action space is just Game Boy keys. The observation space use the \href{https://datacrystal.romhacking.net/wiki/Pok\%C3\%A9mon_Gold_and_Silver:RAM_map}{RAM Map} to read game status.}
          \resumeItem{The agent now can use BFS to traverse the map, the next step is to use PPO algorithm to train the bot do more job.}
        \resumeItemListEnd
        \vspace{-13pt}
      \resumeProjectHeading
        {\textbf{Reimplement of WGAN} $|$ \emph{Pytorch | EECS 545 Final Project}}{Fall Semester, 2021}
        \resumeItemListStart
          \resumeItem{Reimplement the Wasserstein Generative Adversarial Network. Train on CelebA, LSUN and animate character sets.}
          \resumeItem{Analysis the loss function of WGAN and porbe into the reason behind its success.}
          \resumeItem{Compare WGAN's FID score with the widely used DCGAN. Show that WGAN do better than DCGAN.}
        \resumeItemListEnd
        % \vspace{-13pt}
      
      % \resumeProjectHeading
      %     {\textbf{Clash Royale Bot} $|$ \emph{Python, Pytorch — Team Project(with classmate for fun)}}{Winter Break, 2021}
      %     \resumeItemListStart
      %       \resumeItem{A bot that can play the game ”Clash Royale” to defeat human player. Still in progress, lots of function not done yet.}
      %       \resumeItem{The program will first detect and localize opponents’ soldiers moving in the map. We use pre-trained parameters provided by Pytorch to reduce training time.}
      %       \resumeItem{The bot will be later developed to play the game on itself. It will place soldiers that can counter opponents' soldiers it detect.}
      %     \resumeItemListEnd 
      %     \vspace{-13pt}
      % \resumeProjectHeading
      %     {\textbf{XDial} $|$ \emph{Python | Personal Project}}{Spring Semester, 2021}
      %     \resumeItemListStart
      %       \resumeItem{A tool to automatic dial-up to 5G Internet using 5G dialing modules and phone cards on computer.}
      %       \resumeItem{Use serials library to recieve and send message to the modules' port. Match input information with regular expression and dial-up to Internet automatically.}
      %       \resumeItem{Use PyQt library to build a basic GUI for the main interface, tray icon and information alertion.}
      %     \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C/C++, JavaScript} \\
     \textbf{Libraries and tools}{: Pytorch, Gym, Gradle, Selenium, Mixin, GRPC} \\
     \textbf{Developing Software}{: VS Code, Jupyter Notebook, Android Studio, Matlab, \LaTeX, git} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
% \section{Leadership / Extracurricular}
%     \resumeSubHeadingListStart
%         \resumeSubheading{Student Science and Technology Innovation Assosiation}{Fall 2020 -- Summer 2021}{President of Competiton Department}{Shanghai Jiaotong University}
%             \resumeItemListStart
%                 \resumeItem{Holding and arranging workshops on technology topics such as algorithms, useful tools and so on.}
%                 \resumeItem{Organize and promote the registrations of different competitons.}
%                 \resumeItem{Organize science and technology competitions in schools.}
%             \resumeItemListEnd
        
%     \resumeSubHeadingListEnd


\end{document}
